Positivity-Preserving Adaptive Runge--Kutta Methods

### 2020-05-11 nusslein_vsrp/latex/overview.tex
add address etc.

\title{Positivity-Preserving Adaptive Runge--Kutta Methods}
\author{Stephan Nüßlein \and Hendrik Ranocha \and David I. Ketcheson}

\makeatletter
\makeatother

@@

>>>>

\newcommand{\orcid}[1]{ORCID:~\href{https://orcid.org/#1}{#1}}
\usepackage{authblk}
\renewcommand\Affilfont{\fontsize{8}{10.8}\selectfont}

\newenvironment{keywords}{\par\textbf{Key words.}}{\par}
\newenvironment{AMS}{\par\textbf{AMS subject classification.}}{\par}

\title{Positivity-Preserving Adaptive Runge--Kutta Methods}
\author[1]{Stephan Nüßlein\thanks{\orcid{0000-0002-2455-4222}}}
\author[1]{Hendrik Ranocha\thanks{\orcid{0000-0002-3456-2277}}}
\author[1]{David I. Ketcheson\thanks{\orcid{0000-0002-1212-126X}}}
\affil[1]{%
King Abdullah University of Science and Technology (KAUST),
Extreme Computing Research Center (ECRC),
Computer Electrical and Mathematical Science and Engineering Division (CEMSE),
Thuwal, 23955-6900, Saudi Arabia}
% \date{May 11, 2020} %TODO

\makeatletter
\hypersetup{pdfauthor={Stephan Nüßlein, Hendrik Ranocha, David I. Ketcheson}}
\hypersetup{pdftitle={\@title}}
\makeatother

@@

\begin{keywords}
  positivity preserving,
  bound preserving,
  Runge--Kutta methods,
  linear programming
\end{keywords}

\begin{AMS}
  65L06,  % NA, ODEs: Multistep, Runge-Kutta and extrapolation methods
  65L20,  % NA, ODEs: Stability and convergence of numerical methods
  65M12   % NA, PDEs, IVPs, IBVPs: Stability and convergence of numerical methods
\end{AMS}
